Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-23 Ch1_movement_rates/Ch1_Figures.Rmd
Progress with figures.
Modified figure 4 so it only has the dispersion and dispersal per run.

```{r}
disp_df %>% 
  group_by(model) %>% 
  summarise(av.disp = round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1),
            dsprsn = round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1),
            q = c("min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
  pivot_longer(cols = c(av.disp, dsprsn), names_to = "property", values_to = "value") %>% 
  pivot_wider(., names_from = q, values_from = value) %>% 
  arrange(., property) -> qtable_models

@@

Too many points, since we have 500k seeds, show only a percentage.

@@

```{r fig.width=9, fig.height=4}

disp_df %>%
  group_by(., model) %>%
  sample_n(., 10000) %>%
  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Dispersion in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 10000) %>%
  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model
                #, color = dispcat
                )) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal per run in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersal

disp2_plot <- plot_grid(p_dispersal, p_dispersion, ncol = 2, labels = c("B", "C"))
#disp2_plot

@@

```{r fig.height=7.5, fig.width=9}
plot_grid(seedplots2d, NULL, disp2_plot, nrow = 3, rel_heights = c(1,0.2,1))

#ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

# Figure 5 - All about the seed dispersal Kernels - Weibull

Here we are using the distance of each seed

>>>>

disp_df %>% 
  group_by(model) %>% 
  summarise(av.disp = c(mean(av.disp), sd(av.disp), n(), round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1)),
            dsprsn = c(mean(dsprsn), sd(dsprsn), n(), round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1)),
            q = c("mean", "sd", "n", "min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
  pivot_longer(cols = c(av.disp, dsprsn), names_to = "property", values_to = "value") %>% 
  pivot_wider(., names_from = q, values_from = value) %>% 
  arrange(., property) -> qtable_models

@@

```{r fig.width=9, fig.height=3}

disp_df %>%
  group_by(., model) %>%
  ggplot(., aes(x = dsprsn, y = factor(model, levels = c("NP", "PP", "CP")))) +
  geom_violin(color = my.cols1[7], fill = my.cols1[7]) +
  geom_boxplot(width = 0.1, color = "black") +
  labs(x = "Dispersion per run (m)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.y = element_blank()) -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  ggplot(., aes(x = av.disp, y = factor(model, levels = c("NP", "PP", "CP")))) +
  geom_violin(color = my.cols1[7], fill = my.cols1[7]) +
  geom_boxplot(width = 0.1, color = "black") +
  #geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(x = "Average dispersal per run (m)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.y = element_blank()) -> p_dispersal

disp2_plot <- plot_grid(p_dispersal, p_dispersion, ncol = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)

disp2_plot
ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

# Thinking about the long distance or spread: visualize or focus on the 90th percentile data?

Figure 5 - Dispersal for each seed and dispersal kernels

@@

```{r fig.height=7.5, fig.width=9, eval = FALSE}
plot_grid(seedplots2d, NULL, disp2_plot, nrow = 3, rel_heights = c(1,0.2,1))

ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@
